---
title: "Appendiceal-neoplasm"
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding,
      output_file = paste0(dirname(inputFile),'/README.md')) })
output: github_document
---

<i> Analysis and visualization developed by [Luis A. Figueroa](https://twitter.com/LuisFig1706)

The purpose of this site is to make our meta-analysis as transparent as possible. All information or documents used, from the protocol to the final publication, will be available here. If further information is needed, please do not hesitate to contact us.

```{r packages, include=FALSE}
library(metafor)
library(openxlsx)
library(forestplot)
library(dplyr)

knitr::opts_chunk$set(fig.path = "Dic Output Figures/", dev='svg') # dev = 'png'

```

```{r cleaning of Dichotomus outcomes, include=FALSE}
dat <- read.xlsx("Data extraction.xlsx", sheet = 3)
data <- dat[-c(2:5),-c(5,11)]
rownames(data) <- NULL
names(data) <- c('author', 'int', 'comp', 'outc', 'tpart', 'n1', 'n2', 'e1', 'e2')
table(data$author)
data$author[data$author == '1503'] <- 'Westfall, et. al'
data$author[data$author == '188'] <- 'Bolmers, et. al'
data$author[data$author == '823'] <- 'Lietzén, et. al'
data$author[data$author == '841'] <- 'Loftus, et. al'
data$author[data$author == '36'] <-'Alajääski et. al'
data$author[data$author == '213'] <- 'Brunner et. al'
data$author[data$author == '1360'] <- 'Sugimoto et. al'
  
```

```{r or_dichotomus outcomes_adverse effects, include=FALSE}
dat_an <- escalc(measure="OR", ai=n1, bi=n2,
              ci=e1, di=e2, data=data)
dat_an <- summary(dat_an)

```

```{r meta_dichotomus outcomes, include=FALSE}
meta_datan_reml <- rma(yi, vi, method="REML", data=dat_an, test='knha')

```

```{r predict_dichotomus outcomes, include=FALSE}
meta_an <- predict(meta_datan_reml, transf = exp, digits = 2)

```

<br>
<h2>Appendiceal-neoplasm Dichotomus Data</h2>


<details>

<summary><b>Figure A -</b> Appendiceal neoplasm with complicated vs uncomplicated apendicitis </summary>
<br>

```{r graph_REML, echo=FALSE, fig.height = 2.8, fig.width = 15.6}
col1f <- c("Author", dat_an$author, 
      paste("Overall Odds Ratio for", meta_datan_reml$k, "studies"),
      paste("(Tau^2 = ", (formatC(meta_datan_reml$tau2, digits=2, format="f")), ", df = ", 
            (meta_datan_reml$parms),
            ", p ", (ifelse(meta_datan_reml$QEp < 0.001, 
                            paste("< 0.001"),
                            paste("= ", formatC(meta_datan_reml$QEp, digits=3, format="f")))),
            "; ", "I^2", " = ", (formatC(meta_datan_reml$I2, digits=1, format="f")), "%)"))

col2f <- c("Complicated appendicitis (n/N)",
      paste(dat_an$e1,"/", dat_an$n1), paste0(sum(dat_an$e1), " / ", sum(dat_an$n1)), NA)

col3f <- c("Non-complicated appendicitis (n/N)",
      paste(dat_an$e2,"/", dat_an$n2), paste0(sum(dat_an$e2), " / ", sum(dat_an$n2)), NA)


col4f <- c("Odds Ratio (95% CI)", paste0(formatC(exp(dat_an$yi), digits = 2, format = "f"), 
                                        " ( ",formatC(exp(dat_an$ci.lb), format='f', digits=2),
                                        " - ", formatC(exp(dat_an$ci.ub), format='f',digits=2), " ) "),
          paste(formatC(meta_an$pred, format = 'f', digits=2),
            "(", formatC(meta_an$ci.lb, format = 'f', digits = 2),
            "-", formatC(meta_an$ci.ub, format = 'f', digits = 2), ")"), NA)

col5f <- c("Weight(%)", paste(formatC(weights(meta_datan_reml), format='f', digits = 1),'%'), NA, NA)

text1f <- cbind(col1f, col2f, col3f, col4f, col5f)

cf <- structure(list(
          mean = c(NA, exp(dat_an$yi), meta_an$pred, NA),
          lower = c(NA, exp(dat_an$ci.lb), meta_an$ci.lb, NA),
          upper = c(NA, exp(dat_an$ci.ub), meta_an$ci.ub, NA)),
          .Names = c("mean", "lower", "upper"),
          row.names = c(NA, -1L*nrow(text1f)),
          class = "data.frame")

sizes1f <- c(NA, (weights(meta_datan_reml)*0.014), 1, NA)
names(sizes1f) <- NULL

plotf <- forestplot(text1f, 
             graph.pos = 4,
             zero = 1,
             cf,
             new_page = TRUE,
             colgap = unit(5, "mm"),
             hrzl_lines = list("2" = gpar (lwd=1, columns=1:6, col="black")),
             lineheight=unit(0.7,'cm'),
             boxsize = sizes1f,
             is.summary = c(T, rep(F, 6), T, T),
             align = c('l', rep('c', 2), 'l', 'l'),
             ci.vertices = TRUE,
             txt_gp = fpTxtGp(label = gpar (cex=0.9), 
                              ticks = gpar(cex = 0.9, fontface="bold"),
                              summary = gpar(cex = 0.9),
                              xlab = gpar(cex=0.9)),
             xticks = c(0.02, 0.1, 0.3, 1, 2.6, 5.2),
             xlog=TRUE,
             clip = c(0.02, 5.2),
             grid = c(0.02, 0.1, 0.3, 2.6, 5.2),
             lwd.xaxis = 1,
             lwd.ci = 2.2,
             lwd.zero = 2,
             graphwidth = unit(10,"cm"),
             col=fpColors(box="black",line="grey", zero = 'dodgerblue4', axes="grey20", summary="black"))
plotf

```

</details>

